### 2024-08-26 manuscript.tex
Multiple updates

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
simulator. It performs radiative transfer calculations to derive equivalent
lidar backscattered radiation in an atmospheric model, which can then
be compared with observed lidar backscatter \citep{kuma2021}. For this purpose,
it takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
temperature and pressure fields as an input and can be run offline (on the
model output rather than inside the model code). The lidar simulator in the
ALCF is based on the instrument simulator Cloud Feedback Model
Intercomparison Project (CFMIP) Observation Simulator Package (COSP)
\citep{bodas-salcedo2011}. After the backscattered radiation is calculated, a
cloud mask, cloud occurrence by height and the total cloud fraction are
determined.

ALCF has already been used by several research teams for model and reanalysis
evaluation
\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.

@@

% TODO: Describe absolute calibration.

@@

% TODO: Describe absolute calibration.
% TODO: Check sampling rate.

@@

We used a cyclone tracking algorithm to identify extratropical and polar
cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
for the purpose of partitioning the cloud occurrence data into cyclonic and
non-cyclonic conditions. We used the open source package CyTRACK
\citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
We used the mean sea level pressure field and horizontal wind speed fields
as input to the CyTRACK algorithm. The algorithm uses pressure and wind
speed thresholds as well as tracking across time steps to identify cyclone
centres and radii.

@@

\subsection{Cloud occurrence}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/clt_hist.pdf}
\caption{
Daily total cloud fraction histograms calculated as the average of all voyage
and station histograms. The total cloud fraction of a day (UTC) is calculated
as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
lidar profiles. The models and subsets are as in Fig.
\ref{fig:cloud-occurrence}.
}
\label{fig:clt-hist}
\end{figure}

@@

We analysed about 2300 radiosonde proﬁles south of 40°S from the 24 RV
\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.

voyages between the observations and the model. Proﬁles in the model were taken
at the same geographical location and time relative to the start of the year.
Only proﬁles for which the sea ice conditions (sea ice present or absent) are
the same in the observations and the model were included. We derived potential
temperature profiles, lifting condensation level (LCL), and aggregated the
profiles by sea ice conditions (Fig. \ref{fig:radiosonde}).

We found that the variability of potential temperature in the model to be
smaller than in the observations. This indicates that the model does not
represent the entire natural variability. The LCL peaks at the surface in the
observations, but the peak in the model is higher (about 200 m). This probably
relates to the greater occurrence of fog and the peak of cloud occurrence at
the surface in observations, whereas in the model the peak is higher.

\subsection{Cloud occurrence by cyclonic conditions}

\begin{figure}
\centering
\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
\caption{
Virtual potential temperature ($\theta_v$) and relative humidity (RH)
determined from radiosonde launches and co-located profiles in
ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
The solid lines are the average calculated from the averages of every
individual voyage and station. The bands span the
16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
of the voyage and station averages.
}
\label{fig:theta-hur}
\end{figure}

\section{Discussion}

@@

\section{Conclusions}

@@

The ALCF is open source and is available at \url{https://alcf.peterkuma.net}.
cl2nc is open source and is available at
\url{https://github.com/peterkuma/cl2nc}, Our processing a plotting code is
open source and available at
\url{https://github.com/peterkuma/icon-so-2024-code}.

>>>>

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
simulator. It performs radiative transfer calculations to derive equivalent
lidar backscattered radiation in an atmospheric model, which can then
be compared with observed lidar backscatter \citep{kuma2021}. For this purpose,
it takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
temperature and pressure fields as an input and can be run offline (on the
model output rather than inside the model code). The lidar simulator in the
ALCF is based on the instrument simulator Cloud Feedback Model
Intercomparison Project (CFMIP) Observation Simulator Package (COSP)
\citep{bodas-salcedo2011}. After the backscattered radiation is calculated, a
cloud mask, cloud occurrence by height and the total cloud fraction are
determined. ALCF has already been used by several research teams for model and
reanalysis evaluation
\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
Absolute calibration of the observed backscatter was performed by comparing
the measured clear-sky molecular backscatter statistically with simulated
clear-sky molecular backscatter.

@@

@@

% TODO: Check sampling rate.

@@

We partitioned our data into subsets by cyclonic activity. For this purpose,
we used a cyclone tracking algorithm to identify extratropical and polar
cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
We used the open source cylone tracking package CyTRACK
\citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
We used the mean sea level pressure field and horizontal wind speed fields as
input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
thresholds as well as tracking across time steps to identify cyclone centres
and radii. From this information, we could classify geographical areas as
either cyclonic or non-cyclonic. Due to a relatively small total area covered,
we chose a circle of a double radius (relative to one identified by CyTRACK)
centred at the cyclone centre as a cyclonic area for every time step and
cyclone. All other areas were identified as non-cyclonic.  For identifying
cyclones in the observations, ERA5 pressure and wind fields were used as the
input to CyTRACK. This is justified by the fact that large-scale pressure and
wind fields are likely sufficiently close to the reality in ERA5. For
identifying cyclones in ICON, ERA5, MERRA-2, their own pressure and wind fields
were used as the input to CyTRACK.

@@

\subsection{Cloud occurrence by height}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/clt_hist.pdf}
\caption{
Daily total cloud fraction histograms calculated as the average of all voyage
and station histograms. The total cloud fraction of a day (UTC) is calculated
as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
lidar profiles. The models and subsets are as in Fig.
\ref{fig:cloud-occurrence}.
}
\label{fig:cloud-cover}
\end{figure}

\subsection{Cloud cover}

We analysed daily cloud cover (total cloud fraction) distribution. This is a
measure of cloudiness irrespective of height. A cloud detected at any height
means that the lidar profile was classified as cloudy, otherwise it was
classified as clear sky. When all profiles in a day are aggregated together,
the cloud cover for the day is determied as the fraction of cloudy profiles in
the total number of profiles, expressed in octas.

In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets as
anlysed above. Observations show the greatest representation of high cloud
cover (5--8 octas), peaking at 7 octas. This is not represented by ICON or the
reanalyses.  While ICON is the closest, it tends to be 1 octa clearer the
observations, peaking at 6 octas, and highly understimating days with 8 octas.
Overall, the reanalyses show results similar to each other, underestimating
cloud cover by about 2 octas, and strongly understimating days with 7 and 8
octas. Of the two reanalyses, MERRA-2 shows slightly higher cloud cover and
thus more consistent with observations.

When analysed by subsets, the cyclonic subset show to highest cloud cover, with
8 octas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).  This
is not represented by ICON or the reanalyses at all. Interestingly, clear sky
days (0 octas) also have a local maximum peaking at about 15\% in this subset.
When we contrast the low and high latitude zones, we see that the high latitude
zone tends to have greater cloud cover, peaking at 8 octas (Fig.
\ref{cloud-cover}c). The high latitue also has almost no clear sky or small
cloud cover cases (0--4 octas). ICON and the reanalyses represent at least this
charactertic of the distribution well for 0--3 octas, but otherwise show bises
similar to the general case. One of the greatest biases is present in ERA5 in
the unstable subset, where it peaks at 3 octas, whereas the observations peak
at 7 octas and show negligible cloud cover below 5 octas.

@@

We analysed about 2300 radiosonde proﬁles south of 40°S from the 24 RV
\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
temporaly colocated profiles were taken from ICON and the reanalyses. Because
the time period of the ICON model output was different from the observations,
model time was chosen to be the same as the radiosonde launch time relative to
the start of the year. The profiles were partitioned into the same subsets as
the lidar observations: all, 40--55°S, 55+°S, cyclonic, non-cyclonic, stable,
and unstable. The groups 40--55°S and 55+°S, cyclonic and non-cyclonic, and
stable and unstable were mutually exclusive in pairs. Apart from relative
humidity, we focus on comparing virtual potential temperature ($\theta_v$) due
to its role in low-level tropospheric stability, being one of the primary
factors affecting shallow convection and the associated low-level cloud
formation and dissipation. The observed and model profiles of virtual potential
temperature are shown in Fig. \ref{fig:potential-temperature}.

Overall, the mean $\theta_v$ is relatively well represented in ICON and MERRA-2,
being only slightly colder in the mid-to-high troposophere (less stable) in ICON
than in observations (Fig. \ref{fig:potential-temperature}a). Large differences exist, however, exist in the 40--55°S
zone, where ICON is colder in $\theta_v$ by up to about 5 K and more so
at higher altitudes (Fig. \ref{fig:potential-temperature}b). In other subsets, the bias is relatively small. MERRA-2
is very close to the observations, possibly due to a high accuracy of
assimilation of this quantity. Notably, the variability of virtual potential
temperature (as represented by the percentiles) is much smaller in ICON than in
the observations. This indicates that the model's internal variability in the
lower-tropospheric thermodynamic conditions in the SO is smaller then in the
reality.

Relative humidity displays much larger biases. In all subsets, ICON is too
humid in the first 1 km, but very accorate above, except for the 40--55°S zone
and unstable conditions (Fig. \ref{fig:potential-temperature}b, g),  where it
is too dry between about 1 and 3 km. MERRA-2, on the other hand, is much more
humid then observations at all altitudes and in all subsets, by up to about
20\% at 5 km.

\begin{figure}
\centering
\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
\caption{
Virtual potential temperature ($\theta_v$) and relative humidity (RH)
determined from radiosonde launches and co-located profiles in
ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
The solid lines are the average calculated from the averages of every
individual voyage and station. The bands span the
16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
of the voyage and station averages.
}
\label{fig:potential-temperature}
\end{figure}

\section{Discussion and conclusions}

@@

@@

The ALCF, cl2nc, rstool, and our plotting code are open source and available at
\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
\url{https://github.com/peterkuma/rstool}, and
\url{https://github.com/peterkuma/icon-so-2024-code}, respectively. CyTRACK
is available at \url{https://github.com/apalarcon/CyTRACK}.
